???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-24 article.tex
methods save

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \autocite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
\newline
A vineyard's region predetermines several physical parameters, such as: climate, geology and soil; making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. 
%
%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
% What the hell is a regional strategy
% And how do you define, or know what trategy each region is using?
%
Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

@@

\subsubsection{A figure sub-subsection}

@@

\subsection{Data}
The Australian wine industry is divided into 65 regions, known as a Geographical Indicator Regions (GI Region). Each GI Region is used to describe different unique localised traits of vineyards across Australia; with each having its own mixture of climatic and geophysical properties \autocite{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \autocite{attorney-generalsdepartmentWineAustraliaCorporation2010}. The climatic properties of a GI Region are summarised by Sustainable Winegrowing Australia (2021), where regions of similar climates are amalgamated together into superset regions. The climatic regions were utilised to illustrate similar trends and explain differences between sets of regions.
The data used in this analysis comes from Sustainable Winegrowing Australia and covers the period 2015 to 2022. The dataset contained 3342 samples across 52 GI Regions and 1072 individual vineyards.

@@

@@

Classification Trees were developed to discern the different practices within regions and climates, 
% Were they? Or was it to discern regional differences and then compare them?
comparing these relationships to those linked to grape quality. This was done using the rparts and caret packages \autocite{kuhnBuildingPredictiveModels2008,terrytherneauRpartRecursivePartitioning2022} in the R statistical programming language (R Core Team, 2021). 
\newline
Three classifications were undertaken for region, climate and grape quality.
% Is this three classifications for each of these, being 9 in total? Or three overall, one for each?
Climate was further classified into two subcategories of rainfall and temperature,
% Why was this done?
resulting in a total of 5 classification trees being created. % You say this too late!
Classification trees were validated using K-fold cross validation.% This could be its own section!
 Each model was validated using 10 folds, utilising a random selection of different samples ten separate times to validate each of the  classification trees. A summary confusion matrix was then constructed to show the class bias and overall accuracy of each tree.
 % To what end? Why do we want them to be accurate?? What does this analysis achieve?

@@

\subsection{Climate}
Classifying the SWA climatic categorisation of the given regions had better performance than the GI Regions, with ~41.66\% being classified correctly. These categories were divided into 12 climatic classifications with 3 and 4 separate subsets for rainfall and temperature respectively. The decision tree behaved similarly and over classified climates with higher response rates. The results posed an interesting similarity with grape quality classifier, being influenced predominantly by water and area. The use of fungicide to separate regions that were 'Very dry' and 'Damp' can be considered as indicative of the different practices required due to climatic pressure; fungicides being more prominent in cooler regions with greater rainfall due to the higher risk of disease pressure \autocite{reynoldsManagingWineQuality2010}. % interesting although not really appropriate for the results section.
 This could also potentially explain the use of contractor tractor use to discern differences in grape quality, where the lack of contractor use to prevent disease could have led to lowered quality of grapes.

@@

\section{Discussion}
The difference between grape quality is most notable between warm inland regions and coastal regions such as the Riverland and Coonawarra, respectively. Grape quality is only described by a singular variable within this study, however in reality it is driven by market demand and subject to  complex forces such as international market pressure, fire, pests and disease \autocite{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018} % The original citation included years prior to this dataset just be casreful with this. It is a bit unclear what you are really trying to cite and its relevance. I think it important to chop this up.
The decision trees were able to offer some insights into the factors that influence grape quality and regional contrasts that contribute to different qualities. The most prominent being what readily available resources of each region were, particular the types of water available. % A citation or reference to a study looking at the disparity in wine regions and their resources - or use the data more to describe these regional differences. Is water availability apparent? Do some regions have access to more sohpisticated water sources such as pressurised water etc.
 Heavy water consumption is often linked to the mass production of grapes, % Really? proce it? Where in the results is this really found?? This sounds like a link to your previous paper but you cannot really show this and you do not really produce evidence to support this claim.
 where lower quality grapes are targeted in a quantity over quality strategy. These types of business decisions are unfortunately obfuscated by lack of in-depth data regarding vineyard business plans. 
 % This point is incredibly important but it, itself, is obfuscated by you odd claims that are not supported by facts. Better to talk about how this could improve and the weaknesses than to start spouting unsupported claims.
 Notably the literature shows that there are many complex decisions to be made on the ground depending on many compounding factors that influence both quality and yield \autocite{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}
 % Woah woah woah
%
 % what are these decisions??? Slow down speed gonzales!! This is really interseteing and important. Discuss it, its the discussion! God damn I want to know and I wrote this!.
 %
%
% This is not all one paragraph surely! There are so many ideas here that should be discussed!
%
% This leads heavily into the next paper and shows that natural progression. Especially in the sense of: if regions have so much influences, what determines ones use of water, fertiliser, etc. And, what determines the success financially, in quality or quantity? How are thes evariables interacting! The next paper is less about predicting and much more about what interacts with what? Where as this paper is about how things change over landscapes and what localised events helpe to determine decisions and their outcomes.
%

 . There are also further differences when comparing winegrowers to other agricultural industries as they are vertically integrated within the wine industry, tying them to secondary and tertiary industries, such as wine production, packaging, transport and sales. This results in unique issues, where on-the-ground choices are influenced by other wine industry's decisions, such as the use of sustainable practices in vineyards to sell in overseas markets; notably these interactions are further complicated by some winegrowers being totally integrated into wine companies, while others are not (Knight et al., 2019). 
% This is an interesting point. However it would be better to include other industries, such as the ones you touch on in your previous chapter. If industries such as Sake are similar - how do their decisions effect the outcomes of rice quality and Sake? A point of comparison and difference would be great here! 
 It is incredibly difficult to attribute external business decisions to produced grape quality but it is important to acknowledge that some growers are contracted to produce grapes of a particular grade; it is difficult to know whether another consumer may have graded the grape quality differently paying more or less for the same grapes given the opportunity to purchase them.
% What are these business decisions? Can you give some examples?
 It is difficult to untangle the contributing factors to the success of winegrowers and the quality of grapes produced without further specifics of choices made through out a season \autocite{leileiheFruitYieldPrediction2022}.
% It is difficult yes, but please at least try! Highlight some of these affects, some of these different contributing factors! What did we really learn by doing this? What can someone take away from this and say thank you for? (like Josh said)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
\newline
A vineyard's region predetermines several physical parameters, such as: climate, geology and soil; making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. 
%
%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
% What the hell is a regional strategy
% And how do you define, or know what trategy each region is using?
%
Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

@@

@@

\subsection{Data}
The Australian wine industry is divided into 65 regions, known as a Geographical Indicator Regions (GI Region). Each GI Region is used to describe different unique localised traits of vineyards across Australia; with each having its own mixture of climatic and geophysical properties \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. The climatic properties of a GI Region are summarised by Sustainable Winegrowing Australia (2021), where regions of similar climates are amalgamated together into superset regions. The climatic regions were utilised to illustrate similar trends and explain differences between sets of regions.
The data used in this analysis comes from Sustainable Winegrowing Australia and covers the period 2015 to 2022. The dataset contained 3342 samples across 52 GI Regions and 1072 individual vineyards.

@@

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide a both high predictive performance and ability to effectively capture complex relationships. A separate XGBoosted tree was used to predict each variable. As variables were both continuous, binary and multiclass, separate functions were created to handle the three types of variables.

%
With judicious choices for , we may express a variety of tasks, such as regression, classification, and ranking. The task of training the model amounts to finding the best parameters that best fit the training data and labels

. In order to train the model, we need to define the objective function to measure how well the model fit the training data.

A salient characteristic of objective functions is that they consist of two parts: training loss and regularization term:
$obj(\theta)=L(\theta)+\Omega(\theta)$

where $L$ is the training loss function, and $\Omega$ is the regularization term. The training loss measures how predictive our model is with respect to the training data. A common choice of $L$ is the mean squared error, which is given by

$L(\theta)=\sum_i (y_i - \hat{y_i})^2$

Another commonly used loss function is logistic loss, to be used for logistic regression:

The regularization term is what people usually forget to add. The regularization term controls the complexity of the model, which helps us to avoid overfitting. This sounds a bit abstract, so let us consider the following problem in the following picture. You are asked to fit visually a step function given the input data points on the upper left corner of the image. Which solution among the three do you think is the best fit?

% For a given data set with n examples and m features
% D = {(xi, yi)} (|D| = n, xi ∈ Rm, yi ∈ R), a tree ensem-
% ble model (shown in Fig. 1) uses K additive functions to
% predict the output.

\[ \hat{y_i}=\phi(x_i)=\sum_{k=1}^{K}{f_{K}(x_{i})}, f_{K}\in \mathcal{F} \]

%

XGBoosted Regression trees were used to predict continuous variables. With data being split into 80\% training data and 20\% testing data.

XGBoosted classification trees were used to classify the binary and multiclass variables. Data was split into 80\% training, 10\% testing and 10\% validation data.

The modelled relationships are able to be scrutinised by using techniques such as feature importance analysis. The use of the XGBoost library also incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyper-parameters when selecting the final model.

@@

Classification Trees were developed to discern the different practices within regions and climates, 
% Were they? Or was it to discern regional differences and then compare them?
comparing these relationships to those linked to grape quality. This was done using the rparts and caret packages \citep{kuhnBuildingPredictiveModels2008,terrytherneauRpartRecursivePartitioning2022} in the R statistical programming language (R Core Team, 2021). 
\newline
Three classifications were undertaken for region, climate and grape quality.
% Is this three classifications for each of these, being 9 in total? Or three overall, one for each?
Climate was further classified into two subcategories of rainfall and temperature,
% Why was this done?
resulting in a total of 5 classification trees being created. % You say this too late!
Classification trees were validated using K-fold cross validation.% This could be its own section!
 Each model was validated using 10 folds, utilising a random selection of different samples ten separate times to validate each of the  classification trees. A summary confusion matrix was then constructed to show the class bias and overall accuracy of each tree.
 % To what end? Why do we want them to be accurate?? What does this analysis achieve?

@@

\subsection{Climate}
Classifying the SWA climatic categorisation of the given regions had better performance than the GI Regions, with ~41.66\% being classified correctly. These categories were divided into 12 climatic classifications with 3 and 4 separate subsets for rainfall and temperature respectively. The decision tree behaved similarly and over classified climates with higher response rates. The results posed an interesting similarity with grape quality classifier, being influenced predominantly by water and area. The use of fungicide to separate regions that were 'Very dry' and 'Damp' can be considered as indicative of the different practices required due to climatic pressure; fungicides being more prominent in cooler regions with greater rainfall due to the higher risk of disease pressure \citep{reynoldsManagingWineQuality2010}. % interesting although not really appropriate for the results section.
 This could also potentially explain the use of contractor tractor use to discern differences in grape quality, where the lack of contractor use to prevent disease could have led to lowered quality of grapes.

@@

\section{Discussion}
The difference between grape quality is most notable between warm inland regions and coastal regions such as the Riverland and Coonawarra, respectively. Grape quality is only described by a singular variable within this study, however in reality it is driven by market demand and subject to  complex forces such as international market pressure, fire, pests and disease \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018} % The original citation included years prior to this dataset just be casreful with this. It is a bit unclear what you are really trying to cite and its relevance. I think it important to chop this up.
The decision trees were able to offer some insights into the factors that influence grape quality and regional contrasts that contribute to different qualities. The most prominent being what readily available resources of each region were, particular the types of water available. % A citation or reference to a study looking at the disparity in wine regions and their resources - or use the data more to describe these regional differences. Is water availability apparent? Do some regions have access to more sohpisticated water sources such as pressurised water etc.
 Heavy water consumption is often linked to the mass production of grapes, % Really? proce it? Where in the results is this really found?? This sounds like a link to your previous paper but you cannot really show this and you do not really produce evidence to support this claim.
 where lower quality grapes are targeted in a quantity over quality strategy. These types of business decisions are unfortunately obfuscated by lack of in-depth data regarding vineyard business plans. 
 % This point is incredibly important but it, itself, is obfuscated by you odd claims that are not supported by facts. Better to talk about how this could improve and the weaknesses than to start spouting unsupported claims.
 Notably the literature shows that there are many complex decisions to be made on the ground depending on many compounding factors that influence both quality and yield \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}
 % Woah woah woah
%
 % what are these decisions??? Slow down speed gonzales!! This is really interseteing and important. Discuss it, its the discussion! God damn I want to know and I wrote this!.
 %
%
% This is not all one paragraph surely! There are so many ideas here that should be discussed!
%
% This leads heavily into the next paper and shows that natural progression. Especially in the sense of: if regions have so much influences, what determines ones use of water, fertiliser, etc. And, what determines the success financially, in quality or quantity? How are thes evariables interacting! The next paper is less about predicting and much more about what interacts with what? Where as this paper is about how things change over landscapes and what localised events helpe to determine decisions and their outcomes.
%

 . There are also further differences when comparing winegrowers to other agricultural industries as they are vertically integrated within the wine industry, tying them to secondary and tertiary industries, such as wine production, packaging, transport and sales. This results in unique issues, where on-the-ground choices are influenced by other wine industry's decisions, such as the use of sustainable practices in vineyards to sell in overseas markets; notably these interactions are further complicated by some winegrowers being totally integrated into wine companies, while others are not (Knight et al., 2019). 
% This is an interesting point. However it would be better to include other industries, such as the ones you touch on in your previous chapter. If industries such as Sake are similar - how do their decisions effect the outcomes of rice quality and Sake? A point of comparison and difference would be great here! 
 It is incredibly difficult to attribute external business decisions to produced grape quality but it is important to acknowledge that some growers are contracted to produce grapes of a particular grade; it is difficult to know whether another consumer may have graded the grape quality differently paying more or less for the same grapes given the opportunity to purchase them.
% What are these business decisions? Can you give some examples?
 It is difficult to untangle the contributing factors to the success of winegrowers and the quality of grapes produced without further specifics of choices made through out a season \citep{leileiheFruitYieldPrediction2022}.
% It is difficult yes, but please at least try! Highlight some of these affects, some of these different contributing factors! What did we really learn by doing this? What can someone take away from this and say thank you for? (like Josh said)
